### 2016-10-03 Manuscript/SW_early_life_telomeres_SOM.Rmd
Edits

```{r Table S2}
temp <- dd3

#Run the model
lm1 <- lmer(DeltaRTL ~ Agemonths*(Tarsus + Helper + NonHelper + Sex + BodyMass  + TQ) + (1|BirdID) + (1|FieldPeriodID) + (1|TerritoryID),
            data = temp,
            REML = FALSE)
lm1 <- standardize(lm1)

@@

>>>>

```{r Table S2}
temp <- dd3
temp <- subset(temp,!is.na(TQ))

#Run the model
lm1 <- lmer(DeltaRTL ~ Agemonths+(DeltaCondition + Sex + TQ) + (1|BirdID) + (1|FieldPeriodID) + (1|TerritoryID),
            data = temp,
            REML = FALSE)

lm1 <- glmer(DeltaRTLF ~ Agemonths+(Tarsus + Helper + Sex + BodyMass +TQ) + (1|TerritoryID) + (1|BirdID),
            data = temp,
            family = 'binomial',
            control = glmerControl(optimizer = 'bobyqa'))

lm1 <- standardize(lm1)
summary(lm1)
confint.merMod(lm1)

@@

ggplot(dd3,aes(x = DeltaMass,y = (DeltaRTL)))+
geom_point()+
stat_smooth(method = 'lm')

### 2016-10-03 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
Edits

temp <- dd3
temp[,'Age (months)'] <- factor(temp$Agemonths)

Fig4A <- ggplot(temp,
       aes(x = RTL,
           y = RTL1,
           col = factor(DeltaRTLF))) +
  ylab('Adult RTL') + 
  xlab('juvenile RTL') +
    xlim(c(0,3))+
  ylim(c(0,3))+
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_text(size = 12),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
  geom_abline(slope = 1,intercept = 0,lty = 2)+
  geom_point()+
  scale_colour_manual(values = c('navy','red'))+
  annotate('text',x = 0,y = 3,label = 'A')

temp <- subset(dd,DeltaAge !=0)
reps <- tapply(temp$RTL,temp$BirdID,length)
keep <- names(reps[reps>3])
temp <- subset(temp,BirdID %in% keep)
 temp <- subset(temp,!duplicated(paste0(BirdID,Agemonths)))

 mins <- tapply(temp$Agemonths,temp$BirdID,min)
 keep2 <- names(mins[mins <5])
 temp <- subset(temp,BirdID %in% keep2)

@@

Fig4B <- ggplot(temp,aes(x = Agemonths,y = RTL,group = BirdID,col=factor(BirdID)))+
geom_line(col = 'darkgrey')+
  xlab('Age (years)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  #scale_colour_brewer(palette = 'Set1')+
  annotate('text',x = 0,y = 2,label = 'B')

@@

>>>>

temp <- subset(dd3,Agemonths<12)
temp[,'Age (months)'] <- factor(temp$Agemonths)

Fig4A <- ggplot(temp,
       aes(x = RTL,
           y = RTL1)) +
  ylab('Adult RTL') + 
  xlab('juvenile RTL') +
    xlim(c(0,3))+
  ylim(c(0,3))+
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_text(size = 12),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
  geom_abline(slope = 1,intercept = 0,lty = 2)+
  geom_point()+
  scale_colour_manual(values = c('navy','red'))+
  annotate('text',x = 0,y = 3,label = 'A')

temp <- subset(dd,Age<15)
reps <- tapply(temp$RTL,temp$BirdID,length)
keep <- names(reps[reps>0])
temp <- subset(temp,BirdID %in% keep)
 temp <- subset(temp,!duplicated(paste0(BirdID,Agemonths)))

 mins <- tapply(temp$Agemonths,temp$BirdID,min)
 keep2 <- names(mins[mins <400])
 temp <- subset(temp,BirdID %in% keep2)

@@

Fig4B <- ggplot(temp,aes(x = Agemonths,y = RTL,group = BirdID,col=factor(BirdID)))+
  geom_point(alpha = 1,col='grey')+
geom_line(col = 'darkgrey',alpha = 0.2)+
  xlab('Age (years)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  #scale_colour_brewer(palette = 'Set1')+
  annotate('text',x = 0,y = 3,label = 'B')

@@

temp <- subset(dd,Age<15)
reps <- tapply(temp$RTL,temp$BirdID,length)
keep <- names(reps[reps>2])
temp <- subset(temp,BirdID %in% keep)
 temp <- subset(temp,!duplicated(paste0(BirdID,Agemonths)))

ggplot(temp,aes(x = CatchYear,y = RTL,group = BirdID,col=factor(BirdID)))+
  geom_point(alpha = 1,col='grey')+
geom_line(col = 'darkgrey',alpha = 0.2)+
  xlab('Age (years)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  #scale_colour_brewer(palette = 'Set1')+
  annotate('text',x = 1997,y = 2,label = 'B')

ggplot(ddL,aes(x = DeltaRTL,y = RTL,col = Group))+
geom_point()+
stat_smooth(method = 'lm')
